\section{Motivation of this chapter}
In Section \ref{sec:cyclic_B(n)}, we gave a 
sheafy-cyclic object in dg cocategories. 
We would like to extend that construction 
to a sheafy-cyclic object in the 
category of dg cocategories with a dg 
comodule. Namely, we would like to give 
a functor from $\chi$ to $\mathcal{D}$ 
where $\mathcal{D}$ is as follows:
\begin{align*}
Obj(\mathcal{D}) 
&= 
\{(B,C) |
  \textrm{B is a dg cocategory, 
  C is a dg comodule over B}\} \\
\mathcal{D}((B_1, C_1), (B_0, C_0))  
&= 
\{(f, f_!) | f:B_1 \to B_0 
  \textrm{ is a functor,}\\
& \phantom{{}=[(f, f_!)]{}}  
  f_!:C_1 \to f^*C_0 
  \textrm{ is a map of dg comodules over }
  B_1\}
\end{align*}
\begin{align*}  
\mathcal{D}((B_2, C_2), (B_1, C_1)) \times  
\mathcal{D}((B_1, C_1), (B_0, C_0))
&\xrightarrow{composition}
\mathcal{D}((B_2, C_2), (B_0, C_0))\\
(f,f_!) \times (g, g_!)
&\mapsto
(gf, f^*(g_!)\circ f_!)
\end{align*}
(Proposition \ref{prop:pbs_compose} implies 
that composition in $\mathcal{D}$ is 
associative.)

In Section \ref{sec:shriek_maps}, we 
gave maps $\lambda_!: C(\mathcal{A}) 
\to \hat{\lambda}^*C(\mathcal{A}^\prime)$ 
for $\mathcal{A}, \mathcal{A}^\prime \in 
Obj(\chi)$ and $\lambda$ a generating 
morphism in $\Lambda$ that induces a 
morphism in $\chi(\mathcal{A}, 
\mathcal{A}^\prime)$. Ideally, these 
$\lambda_!$ would give a functor 
$\chi \to \mathcal{D}$, but 
unfortunately, they only respect 
composition up to homotopy. Fortunately, 
most of the compositions are respected 
and, for the ones that are not, we 
have explicit homotopies. Our homotopies 
will commute with the original 
$\lambda_!$'s so that no higher homotopies 
are needed.

In this chapter, we will show which compositions 
are respected on the nose and which ones 
need homotopies. We will then give these homotopies 
and show that no higher homotopies are 
needed. This chapter is the computational 
heart of this thesis. The next chapter will 
repackage this ``functor up to homotopy'' 
in more abstract terms.